Holomorphic field theories and higher algebra

### 2025-01-10 draft_preMinyong.tex
o begins to implememt minhyongs suggestions

As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
(For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
and this derived moduli space encodes solutions to
a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it is due to the original notation people used.}
Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformation quantization); 
the relevant moduli space being the derived mapping space between complex manifolds.

>>>>

As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
(For $Y = V$ a complex vector space, a ``derived'' enhancement includes the higher dimensional  cohomology $H^*(X, \cO) \otimes V$.)
In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
and this derived moduli space encodes solutions to
a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it is due to the original notation people used.}
Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformation quantization); 
the relevant moduli space being the derived mapping space between complex manifolds.
